\documentclass[accentcolor=tud9c,nochapname,11pt]{tudexercise}

%ä <- steht nur hier, damit manche Editoren den Unicode richtig erkennen...
\usepackage{amssymb} % needed for math
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english,ngerman]{babel}
\usepackage{scrhack}
\usepackage{fixltx2e}
\usepackage{microtype}


\linespread{1.1}

\usepackage{hyperref}
\usepackage{booktabs}
\setlength{\parindent}{0pt}
\makeatletter
\newcommand\saferead[1]{%
  \bgroup
  \let\do\@makeother
  \dospecials\catcode`\ 10
  \input{#1}%
  \egroup 
}
\makeatother


\begin{document}

\title{Projektbewirtschaftung \\ Lichtenberg-Rechner}
\subtitle{Project Proposal}
\maketitle
%\chapter{Mein erstes Kapitel}

\begin{itemize}
	\item \textbf{For Test Accounts:} fill in this proposal (you do not need to upload a detailed proposal). Use the comment field (see 4.4) later on to tell us that you only apply for a test account.
	\item Before you submit a new Proposal please fill in at least the project title, section 1.1 (Director), section 1.2 (Principal Investigator), section 1.3 (Manager) and 3.2 (Typical Single Run). Usually projects are required to also fill section 2.1 (Abstract) and section 3.7 (Software).
\end{itemize}

\section{Administrative Details}

\begin{Form}
\begin{tabbing}
xxxxxxxxxxxxxxxxxxx: \= \kill  \\% This is needed for the right tab width
\textbf{Project Title:}  \saferead{proj_title.txt} \\
\textbf{Proposing Institution:}  	\saferead{prop_inst.txt} \\
\textbf{Federal State of the proposing Institution:}    Ireland \\
\end{tabbing}
\subsection{Director of the Institution}
\begin{tabbing}
xxxxxxxxxxxxxxxxxxxxxxxxx:  \= \kill
\textbf{Title:}    \saferead{dir_title.txt} \\
\textbf{Last name:} abcd  \>  \textbf{First name:} defghi  \\
\textbf{Street:} ST.Johns street  \\
\textbf{Postal code:} 64297   \> \textbf{City:} Darmstadt  \\
\textbf{Phone:}+4915xxxxxxxxx  \> \textbf{Fax:}..........   \\
\textbf{Email:} google@outlook.com \\
\end{tabbing}
\subsection{Principal Investigator(If it is not the Director)}
\begin{tabbing}
xxxxxxxxxxxxxxxxxxxxxxxxx:  \= \kill
\textbf{Title:}   Mr. \\
\textbf{Last name:} Foo  \>  \textbf{First name:} bar  \\
\textbf{Street:} James street 10  \\
\textbf{Postal code:} 63287   \> \textbf{City:} Darmstadt  \\
\textbf{Phone:}+4915xxxxxxxxx  \> \textbf{Fax:}..........  \\
\textbf{Email:} google@gmx.com \\
\end{tabbing}
\subsection{Project Manager/Main Researcher}
The Project manager is responsible for the administrative tasks of the project, e.g. distribution und supervision of the granted logins and resources.   \\
\begin{tabbing}
xxxxxxxxxxxxxxxxxxxxxxxxx:  \= \kill
\textbf{Title:}  Mrs. \\
\textbf{Last name:} David  \>  \textbf{First name:} bar  \\
\textbf{Street:} Stadtmitte street 11  \\
\textbf{Postal code:} 63247   \> \textbf{City:} Pfungstadt  \\
\textbf{Phone:}+4915xxxxxxxxx  \> \textbf{Fax:}..........   \\
\textbf{Email:} gmx@yahoo.com \\
\end{tabbing}
\subsection{Researchers}
Please list all persons who need access. List the director (sec. 1.1),Principal Investigator (sec. 1.2), the manager (sec. 1.3), and the researchers (sec. 1.4) if and only if they need an account. All "researchers" will be added to the mailing list hkhlr-users@lists.hrz-darmstadt.de.Please give your professional e-mail address. E-mail addresses such as Gmail and Hotmail are not accepted. \\
\begin{table}[h!]
							\begin{center}
							\begin{tabular}{cccccc}
							\toprule
								Nr & Title & Last name & First name & Phone & E-Mail\\
							\midrule
							  1 & Mr & John & David & +4915124311236 & david.john@gmail.com\\
							\bottomrule
							\end{tabular}
					\end{center}
			\end{table} 
	  	\begin{center}
				\textbf{Gender:} Male \hspace{35pt} \textbf{Nationality(required):} German \hspace{35pt} \textbf{TU-Id:} tr23sd45 \\
				\end{center}}
				\textbf{If you want to use certificates for login, \\
				 enter the distinguished name of the researcher here:} Dr. Foo \hspace{15pt} \CheckBox[name=licht_acc,charsize=12pt,checked]{Lichtenberg account exists ?}	
\begin{table}[h!]
							\begin{center}
							\begin{tabular}{cccccc}
							\toprule
								Nr & Title & Last name & First name & Phone & E-Mail\\
							\midrule
							  2 & Mr & Tom & Jerry & +4915124311236 & jerry.tom@gmail.com\\
							\bottomrule
							\end{tabular}
					\end{center}
			\end{table} 
	  	\begin{center}
				\textbf{Gender:} Male \hspace{35pt} \textbf{Nationality(required):} American \hspace{35pt} \textbf{TU-Id:} tr65sd45 
			\end{center}}			
			\textbf{If you want to use certificates for login, \\
				 enter the distinguished name of the researcher here:} Dr. Foo \hspace{15pt} \CheckBox[name=licht_acc,charsize=12pt,checked]{Lichtenberg account exists ?}	\\
If the fields above are not sufficient for login, you can add further researchers here: \\
\fbox{
	\begin{minipage}{5in}
		\hfill \vspace{2in} \hspace{2in}
	\end{minipage}
	} 
\subsection{Project Partners}
If project partners from outside the proposing institute are involved, please list them here. Project partners will not be granted access to the Lichtenberg Computer unless you specify them as "Researchers" (in section 1.4), too.
\begin{tabbing}
xxxxxxxxxxxxxxxxxxxxxxxxxxxxxx:  \= \kill
\textbf{Title:}   Mr. \> \textbf{Name of the Institute:} Johannesberg institute of applied sciences \\
\textbf{Last name:} Foo  \>  \textbf{First name:} bar  \\
\textbf{Street:} Gutenberger street 10 \> \textbf{Postal code & City:} 63287,Darmstadt  \\
\textbf{Email:} google@gmx.com  \> \textbf{Phone:}+4915xxxxxxxxx     \\
\end{tabbing}
\begin{center}
	\CheckBox[name=tu_id,charsize=12pt,checked]{TU-ID exists?} \hspace{10pt} \CheckBox[name=licht_acc,charsize=12pt,checked]{Lichtenberg account exists ?} \\
\end{center}
If the fields above are not sufficient for login, you can add further researchers here: \\
\fbox{
	\begin{minipage}{5in}
		\hfill \vspace{2in} \hspace{2in}
	\end{minipage}
	} 

\end{Form}
\end{document}